### 2018-01-31 includes/abstract.tex
Pass of paper

\begin{abstract}
    In this paper, we introduce \fuzzer{}: a modular \smt{} problem instance
    transformer and generator for string solvers. We supply a
    repository of instances generated by \fuzzer{} in \smtfull{}
    format. We systematically compare \theSolvers{} on groups of such
    instances, and identify the ones that are particularly challenging for
    some solvers. We briefly explain our observations and show how
    \fuzzer{} helped find causes of performance degradations in
    \us{}.
\end{abstract}

>>>>

\begin{abstract}
    In this paper, we introduce \fuzzer{}: a modular \smt{} problem instance
    transformer and generator. We supply a
    repository of instances generated by \fuzzer{} in \smtfull{}
    format. We systematically compare \theSolvers{} on groups of such
    instances, and identify those that are particularly challenging for
    some solvers. We briefly explain our observations and show how
    \fuzzer{} helped discover causes of performance degradations in
    \us{}.
\end{abstract}

### 2018-01-31 includes/experiment.tex
Pass of paper

We generated several problem instance suites with \fuzzer{} that made one
solver perform poorly, but not others. These suites are
\theSuites{}. Figure~\ref{fig:cvc-hard} shows the suites that were
uniquely difficult for \cvc{}. Figure~\ref{fig:z3str3-hard} shows the
suites that were uniquely difficult for \us{}. All experiments were
run in series, with a timeout of 15 seconds, on the same computer running
Ubuntu Linux 16.04. The computer had 32GB of RAM and an
Intel\textregistered{} Core\texttrademark{} i7-6700 CPU with clock speed
of 3.40GHz.

@@

\fuzzer{}'s ability to produce scaling instances helped uncover several
implementation issues and performance limitations in \us{}. Scaling inputs
can reveal issues that would be out of scope for unit tests or
industrial benchmarks because they elicit asymptotic behaviour. Three different
performance and implementation bugs were identified and fixed in \us{}
as a result of testing with the \fuzzer{} scaling suites
\textit{Lengths} and \textit{Concats}.

We also found a number of performance-related issues and opportunities for
new heuristics in \us{} thanks to \fuzzer{}. For example, the
instances in the \textit{Concats} suite helped us discover a
potential new heuristic. In particular, \us{} didn't
make full use of the solving context (e.g. some terms are empty
strings) to simplify the concatenations of a long list of string terms
before trying to reason about the equivalences among subterms. \us{}
therefore introduced a large number of unnecessary intermediate
variables and propagations. As a consequence of
testing \us{} with the \textit{Concats} suite, we were able to
identify the factors common to its instances, examine \us{}'s execution
traces on them, and rapidly formulate a hypothesis as to why \us{}
was performing poorly.

>>>>

We generated several problem instance suites with \fuzzer{} that made one
solver perform poorly, but not others. These suites are
\theSuites{}. Fig.~\ref{fig:cvc-hard} shows the suites that were
uniquely difficult for \cvc{}. Fig.~\ref{fig:z3str3-hard} shows the
suites that were uniquely difficult for \us{}. All experiments were
conducted in series, each with a timeout of 15 seconds,
on an Ubuntu Linux 16.04 computer with 32GB of RAM and an
Intel\textregistered{} Core\texttrademark{} i7-6700 CPU (3.40GHz).

@@

\fuzzer{}'s ability to produce scaling instances helped uncover several
implementation issues and performance limitations in \us{}. Scaling inputs
can reveal issues that would normally be out of scope for unit tests or
industrial benchmarks. Three different
performance and implementation bugs were identified and fixed in \us{}
as a result of testing with the \fuzzer{} scaling suites
\textit{Lengths} and \textit{Concats}.

\fuzzer also helped identify a number of performance-related issues and opportunities for
new heuristics in \us{}. For example, by examining \us{}'s execution traces on the
instances in the \textit{Concats} suite we discovered a
potential new heuristic. In particular, \us{} does not
make full use of the solving context (e.g. some terms are empty
strings) to simplify the concatenations of a long list of string terms
before trying to reason about the equivalences among sub-terms. \us{}
therefore introduces a large number of unnecessary intermediate
variables and propagations.

### 2018-01-31 includes/introduction.tex
Pass of paper

In recent years, many algorithms for solving string constraints have
been developed and implemented in SMT solvers such as Norn~\cite{norn},
CVC4~\cite{cvc4}, and Z3 (e.g., Z3str2~\cite{z3str2} and Z3str3~\cite{z3str3}).
To validate and benchmark these solvers, their developers have relied on
hand-crafted input suites~\cite{cvc4-tests,z3str3-tests,z3str2-tests} or
real-world examples from a limited set of industrial
applications~\cite{kaluza,kausler}. These test suites have helped
developers identify implementation defects and develop more
sophisticated solving heuristics. Unfortunately, as solvers grow,
fixed benchmarks leave more functionality untested.
There is an acute need for a more robust, inexpensive, and automatic way
of generating benchmarks to test
the correctness and performance of SMT solvers.

Fuzzing is often used to test all kinds of software,
including SAT solvers~\cite{fuzzsat}. Inspired by the utility of fuzzers,
we introduce a fuzzer for string solvers, \fuzzer{}, and describe its value
as an exploratory testing tool. We demonstrate its efficacy
by presenting limitations it helped us find in
leading string solvers. To the best of our knowledge, \fuzzer{} is the
first tool aimed at automatic generation of string constraints. \fuzzer{} can
be used to mutate or transform existing benchmarks, as well as
randomly generate structured instances. These instances can be scaled with
respect to a variety of parameters, e.g., length of string constants,
depth of concats and regeular expressions, number of variables,
number of length constraints, and many more.

@@

\begin{enumerate}
    \item \textbf{The \fuzzer{} tool}:
        In section~\ref{sec:fuzzer}, we describe a modular fuzzer that can
        transform and generate \smtfull{} string and regular
        expression (regex) instances.\footnote{We assume basic
        familiarity with string solvers and their input
        language.} Scaling inputs (e.g., long string constants,
        deep concatenations) are particularly useful in identifying asymptotic
        behaviors in solvers, and \fuzzer{} has many options to generate them.
        We briefly document \fuzzer{}'s components and modular architecture.
        We provide example use cases to demonstrate its utility as an
        exploratory solver testing tool.

    \item \textbf{A repository of \smtfull{} instances}:
        We present a repository of \smtfull{} string and regex instance suites
        we generated using \fuzzer{} in section~\ref{sec:suites}. The
        repository consists of two categories: \texttt{generated}, with new
        instances generated by \fuzzer{}, and \texttt{transformed}, with
        transformed instances generated from a small suite of industrial
        benchmarks.

    \item \textbf{Experimental Results and Analysis}:
        We compare the performance of \theSolvers{} on the
        the \fuzzer{} suites \theSuites{} in section~\ref{sec:data}. We
        highlight these suites because they make some solvers perform poorly,
        but not others. We analyze our
        experimental results, and pinpoint algorithmic limitations
        in \us{} that cause poor performance.
\end{enumerate}

>>>>

In recent years, many algorithms for solving string constraints have
been developed and implemented in SMT solvers such as Norn~\cite{norn},
CVC4~\cite{cvc4}, and Z3 (e.g., Z3str2~\cite{z3str2} and Z3str3~\cite{z3str3}).
To validate and benchmark these solvers, their developers have relied on
hand-crafted input suites~\cite{cvc4-tests,z3str3-tests,z3str2-tests} or
real-world examples from a limited set of industrial
applications~\cite{kaluza,kausler}. These test suites have helped
developers identify implementation defects and develop more
sophisticated solving heuristics. Unfortunately, as solvers grow
fixed benchmarks remain stagnant, leaving increasing functionality untested.
As such, there is an acute need for a more robust, inexpensive, and automatic way
of generating benchmarks to test
the correctness and performance of SMT solvers.

Fuzzing has been used to test all kinds of software
including SAT solvers~\cite{fuzzsat}. Inspired by these fuzzers,
we introduce \fuzzer{} and describe its value
as an exploratory testing tool. We demonstrate its efficacy
by presenting limitations it helped discover in
leading string solvers. To the best of our knowledge, \fuzzer{} is the
only tool aimed at automatic generation of string constraints. \fuzzer{} can
be used to mutate or transform existing benchmarks, as well as
randomly generate structured instances. These instances can be scaled with
respect to a variety of parameters, e.g., length of string constants,
depth of concatenations (concats) and regular expressions, number of variables,
number of length constraints, and many more.

@@

\begin{enumerate}
    \item \textbf{The \fuzzer{} tool}:
        In Sect.~\ref{sec:fuzzer}, we describe a modular fuzzer that can
        transform and generate \smtfull{} string and regular
        expression (regex) instances.\footnote{We assume basic
        familiarity with string solvers and their input
        language.} Scaling inputs (e.g., long string constants,
        deep concatenations) are particularly useful in identifying asymptotic
        behaviors in solvers, and \fuzzer{} has many options to generate them.
        We briefly document \fuzzer{}'s components and modular architecture.
        We provide example use cases to demonstrate its utility as an
        exploratory solver testing tool.

    \item \textbf{A repository of \smtfull{} instances}:
        We present a repository of \smtfull{} string and regex instance suites
        that we generated using \fuzzer{} in Sect.~\ref{sec:suites}. This
        repository consists of two categories: one with new
        instances generated by \fuzzer{} (\texttt{generated}); and another with
        transformed instances generated from a small suite of industrial
        benchmarks (\texttt{transformed}).

    \item \textbf{Experimental Results and Analysis}:
        We compare the performance of \theSolvers{} on the
        the \fuzzer{} suites \theSuites{} in Sect.~\ref{sec:data}. We
        highlight these suites because they make some solvers perform poorly,
        but not others. We analyze our
        experimental results, and pinpoint algorithmic limitations
        in \us{} that cause poor performance.
\end{enumerate}

### 2018-01-31 includes/stringfuzz.tex
Pass of paper

\fuzzer{} is implemented as a Python package, and comes with several
executables to generate, transform, and analyze \smtfull{} string and regex
instances. It can either be installed from source, or from the Python
PIP package repository.\footnote{The link to the
source code will be added after double-blind review.}
\fuzzer{} is organized to be easily extended:
all generators and transformers are independent Python modules. To demonstrate
its modularity, we note that the implementations of transformers in \fuzzer{}
contain \linesPerX{} lines of code on average, whereas the whole fuzzer
contains \linesInFuzzer{} lines. Its components are also
implemented as \unix{} ``filters'', to enable easy
integration with other tools (including themselves). For example, the
outputs of generators can be piped into transformers, and transformers
can be chained to produce a stream of tuned inputs to a
solver. \fuzzer{} is composed of the following tools:
\begin{description}
    \item[\generator{}] \hfill \\
        This tool generates \smt{} instances. It supports several generators and
        options that specify its output. Details can be found in
        table~\ref{tbl:generators}.
    \item[\transformer{}] \hfill \\
        This tool transforms \smt{}
        instances. It supports several transformers and options that specify
        its output and input, which are explained in
        table~\ref{tbl:transformers}. Note that transformers
        \textit{Translate} and \textit{Reverse} also preserve
        satisfiability under certain conditions~\cite{ifaz}.
    \item[\texttt{stringstats}] \hfill \\
        This tool takes an \smt{}
        instance as input and outputs its properties: the number of
        variables/literals, the max/median syntactic depth of expressions, the
        max/median literal length, etc.
\end{description}

\begin{table}[t]
    \centering
    \caption{\generator{} generators.}
    \label{tbl:generators}
    \begin{tabular}{|l|l|}
        \hline
        \textbf{Name}
            & \textbf{Generated instances have ...}
            \\ \hline
        \textit{Concats}
            & Long concats and optional random extracts.
            \\ \hline
        \textit{Lengths}
            & Many variables (and their concats) with length constraints.
            \\ \hline
        \textit{Overlaps}
            & An expression of the form A.X = X.B.
            \\ \hline
        \textit{Equality}
            & An equality among concats, each with variables or constants.
            \\ \hline
        \textit{Regex}
            & Regexes of varying complexity.
            \\ \hline
        \textit{Random-Text}
            & Random, likely syntactically \textit{in}valid text.
            \\ \hline
        \textit{Random-AST}
            & Random, but semantically \textit{valid} text.
            \\ \hline
    \end{tabular}

    \caption{\transformer{} transformers.}
    \label{tbl:transformers}
    \begin{tabular}{|l|l|}
        \hline
        \textbf{Name}
            & \textbf{The transformer ...}
            \\ \hline
        \textit{Fuzz}
            & Randomly replaces literals and operators with similar ones.
            \\ \hline
        \textit{Graft}
            & For each sort, swaps a random non-leaf node with a leaf node.
            \\ \hline
        \textit{Multiply}
            & Multiplies each number by N, and repeats each character N times.
            \\ \hline
        \textit{Nop}
            & Doesn't transform (but can translate \smtfull{}).
            \\ \hline
        \textit{Reverse}
            & Reverses all string literals and concat arguments.
            \\ \hline
        \textit{Rotate}
            & Performs a random syntax tree rotation on two concats.
            \\ \hline
        \textit{Translate}
            & Maps every character X to a different character Y.
            \\ \hline
        \textit{Unprintable}
            & Randomly replaces all characters in literals with unprintable ones.
            \\ \hline
    \end{tabular}
\end{table}

@@

\fuzzer{} can generate
and transform instances with regular expression constraints. The
command \texttt{stringfuzzg regex} invokes the regex instance
generator. It generates a instance of the form:
\begin{align*}
    & \texttt{(assert (str.in.re X}\; R_0\; \texttt{))} \\
    & \texttt{(assert (str.in.re X}\; R_n\; \texttt{))}* \\
    & \texttt{(assert (<= Min (str.len X)))}? \\
    & \texttt{(assert (<= (str.len X)) Max)}?
\end{align*}

@@

where $j$ is the specified depth of recursion. Terms at depth 0 are
regex constants. Informally, this form describes a concatenation of
regex terms, where each term is a random nested regex operator (chosen from
regex Kleene star, repetition, and union), up to a specified depth,
terminating in a regex literal. Below are three example regexes
(separated by spaces) of depth 2 produced by this scheme:
\begin{align*}
  & ((\texttt{a}|\texttt{b})|(\texttt{cc})+)\quad\quad
  ((\texttt{ddd})*)+\quad\quad ((\texttt{ee})+|(\texttt{fff})*)
\end{align*}

\fuzzer{} can also transform the instances it generates. All of the
transformers in \transformer{} can operate on regex terms. They can
multiply and permute regex literals (e.g. \textit{Reverse},
\textit{Multiply}, \textit{Translate}), randomly replace regex
operators (e.g. \textit{Fuzz}), and manipulate the syntax tree
(e.g. \textit{Graft}, \textit{Rotate}).

\subsubsection{Example Use Case}

\fuzzer{} can be used to generate benchmark suites in a batch mode, but also
in an online randomized fashion for exploratory debugging. For example,
\fuzzer{} can be invoked as follows to feed random instances to \cvc{} until it
returns an error:
{\scriptsize\begin{verbatim}
while stringfuzzg -r random-ast -m \
    | tee instance.smt25 | cvc4 --lang smt2.5 --tlimit=5000 --strings-exp; do
    sleep 0
done\end{verbatim}}

>>>>

\fuzzer{} is implemented as a Python package, and comes with several
executables to generate, transform, and analyze \smtfull{} string and regex
instances. Its components are implemented as \unix{} ``filters'' to enable easy
integration with other tools (including themselves). For example, the
outputs of generators can be piped into transformers, and transformers
can be chained to produce a stream of tuned inputs to a
solver. \fuzzer{} is composed of the following tools:

\begin{description}
    \item[\generator{}] \hfill \\
    This tool generates \smt{} instances. It supports several generators and
    options that specify its output. Details can be found in
    Table~\ref{tbl:generators}.
    \item[\transformer{}] \hfill \\
    This tool transforms \smt{}
    instances. It supports several transformers and options that specify
    its output and input, which are explained in
    Table~\ref{tbl:transformers}. Note that transformers
    \textit{Translate} and \textit{Reverse} also preserve
    satisfiability under certain conditions~\cite{ifaz}.
    \item[\texttt{stringstats}] \hfill \\
    This tool takes an \smt{}
    instance as input and outputs its properties: the number of
    variables/literals, the max/median syntactic depth of expressions, the
    max/median literal length, etc.
\end{description}

We organized \fuzzer{} to be easily extended. As evidence of our success we note
that while the whole project 
contains \linesInFuzzer{} lines of code, it takes an average of 
\linesPerX{} lines of code to create a transformer. \fuzzer{} can either be 
installed from source, or from the Python PIP package
repository.\footnote{The link to the source code will be added after double-blind review.}

\begin{table}[t]
    \centering
    \caption{\generator{} built-in generators.}
    \label{tbl:generators}
    \begin{tabular}{|l|l|}
        \hline
        \textbf{Name}
        & \textbf{Generate instances that have ...}
        \\ \hline
        \textit{Concats}
        & Long concats and optional random extracts.
        \\ \hline
        \textit{Lengths}
        & Many variables (and their concats) with length constraints.
        \\ \hline
        \textit{Overlaps}
        & An expression of the form A.X = X.B.
        \\ \hline
        \textit{Equality}
        & An equality among concats, each with variables or constants.
        \\ \hline
        \textit{Regex}
        & Regexes of varying complexity.
        \\ \hline
        \textit{Random-Text}
        & Random, likely syntactically \textit{in}valid text.
        \\ \hline
        \textit{Random-AST}
        & Random, but semantically \textit{valid} text.
        \\ \hline
    \end{tabular}

    \caption{\transformer{} built-in transformers.}
    \label{tbl:transformers}
    \begin{tabular}{|l|l|l|}
        \hline
        \textbf{Name}
        & \textbf{The transformer ...}
        & \textbf{Guarantee}\footnote{See Appendix for proofs and restrictions.}
        \\ \hline
        \textit{Fuzz}
        & Randomly replaces literals and operators with similar ones.
        & Well-formed
        \\ \hline
        \textit{Graft}
        & For each sort, swaps a random non-leaf node with a leaf node.
        & Well-formed
        \\ \hline
        \textit{Multiply}
        & Multiplies each number by N, and repeats each character N times.
        & Sat-sat
        \\ \hline
        \textit{Nop}
        & Does not transform (can translate between \smtfull{}).
        & Equisat
        \\ \hline
        \textit{Reverse}
        & Reverses all string literals and concat arguments.
        & Equisat
        \\ \hline
        \textit{Rotate}
        & Performs a syntax tree rotation on compatible operators.
        & Well-formed
        \\ \hline
        \textit{Translate}
        & Permutes the alphabet.
        & Equisat
        \\ \hline
        \textit{Unprintable}
        & Randomly replaces all characters in literals with unprintable ones.
        & Equisat
        \\ \hline
    \end{tabular}
\end{table}

@@

\fuzzer{} can generate
and transform instances with regular expression constraints. For example, the
command \texttt{stringfuzzg regex} invokes the regex instance
generator and produces an instance of the form:
\begin{align*}
    & \texttt{(assert (str.in.re X}\; R_0\; \texttt{))} \\
    & \texttt{(assert (str.in.re X}\; R_n\; \texttt{))}* \\
    & \texttt{(assert (<= Min (str.len X)))}? \\
    & \texttt{(assert (<= (str.len X)) Max)}?
\end{align*}

@@

where $j$ is the specified depth of recursion. Terms at depth 0 are
regex constants. Informally, this form describes a concatenation of
regex terms, where each term is a random nested regex operator (chosen from
regex Kleene star, repetition, and union), up to a specified depth,
terminating in a regex literal. Below are three example regex instances
(separated by spaces) of depth 2 produced by this scheme:
\begin{align*}
    & ((\texttt{a}|\texttt{b})|(\texttt{cc})+)\quad\quad
    ((\texttt{ddd})*)+\quad\quad ((\texttt{ee})+|(\texttt{fff})*)
\end{align*}

\fuzzer{} can also transform problem instances.
This is done by manipulating parsed syntax trees.
By default most of the built-in transformers 
only guarantee well-formedness, however,
some can even guarantee equisatisfiability. Table~\ref{tbl:transformers} 
lists the built-in transformers and these guarantees.

\subsubsection{Example Use Case}
In Sect.~\ref{sec:suites} we use \fuzzer{} to generate benchmark suites in a batch mode.
We can also use \fuzzer{} for on-line exploratory debugging. 
For example, the script below repeatedly feeds random \fuzzer{} 
instances to \cvc{} until the solver produces an error:
{\scriptsize\begin{verbatim}
while stringfuzzg -r random-ast -m \
    | tee instance.smt25 | cvc4 --lang smt2.5 --tlimit=5000 --strings-exp; do
    sleep 0
done\end{verbatim}}

### 2018-01-31 includes/suites.tex
Adding more data to tables. Formatting tables for easier editing. Adding two more test problems.
Adding citation for FuzzSAT. Fixing up more content.
Pass of paper

In this section, we describe the benchmark suites that we generated
with \fuzzer{}, and on which we conducted our experimental
evaluation.\footnote{The link to the repository will be added after
double-blind review.}

@@

The \textit{Amazon} category contains 472 instances, derived from two seeds
supplied by our industrial collaborators. The \textit{Regex} category is
seeded by the z3str2 regular expression test suite~\cite{z3str2-tests}. This
test suite contains 42 instances dealing with a wide variety of regular
expressions. Through cumulative transformations, we expanded it to 7,551
instances. Finally, the \textit{Sanitizer} category is obtained from
five industrial e-mail address and IPv4 sanitizers.

\begin{table}[t]
    \centering
    \caption{\generator{}-generated instances.}
    \label{tbl:generated}
    \begin{tabular}{|l|l|}
        \hline
        \textbf{Name}             & \textbf{Instances have ...} \\ \hline
        \textit{Concats}          & A right-heavy, deep tree of concats. \\ \hline
        \textit{Concats-Balanced} & A balanced, deep tree of concats. \\ \hline
        \textit{Concats-Extracts} & A single concat tree, and random character extractions. \\ \hline
        \textit{Lengths}          & A single, large length constraint on a variable. \\ \hline
        \textit{Lengths-Concats}  & Variables and their concats, each with fixed lengths. \\ \hline
        \textit{Overlaps}         & A formula of the form A.X = X.B. \\ \hline
        \textit{Regex}            & A test for regex membership of arbitrary complexity. \\ \hline
        \textit{Many-Regexes}     & A test for membership in many random regexes. \\ \hline
        \textit{Regex-Deep}       & A test for membership in a regex with many nested operators. \\ \hline
        \textit{Regex-Pair}       & A test for membership in one regex, but not another. \\ \hline
        \textit{Regex-Lengths}    & A test for membership in a regex, and a length constraint. \\ \hline
    \end{tabular}
\end{table}

\begin{table}[t]
    \centering
    \caption{Transformed instances generated by \transformer{}.}
    \label{tbl:transformed}
    \begin{tabular}{|l|l|r|}
        \hline
        \textbf{Name}      & \textbf{Seed}                             & \textbf{Quantity} \\ \hline
        \textit{Amazon}    & Two industrial regex membership instances & 472 \\ \hline
        \textit{Regex}     & Z3str2 regular expression test suite      & 7,551 \\ \hline
        \textit{Sanitizer} & 5 e-mail and IPv4 sanitiser examples      & 1,170 \\ \hline
    \end{tabular}
\end{table}

>>>>

In this section, we describe the benchmark suites we generated
with \fuzzer{}, and on which we conducted our experimental
evaluation.\footnote{The link to the repository will be added after
double-blind review.}

@@

The \textit{Amazon} category contains 472 instances derived from two seeds
supplied by our industrial collaborators. The \textit{Regex} category is
seeded by the \usOld{} regular expression test suite~\cite{z3str2-tests}. This
test suite contains 42 instances dealing with a wide variety of regular
expressions. Through cumulative transformations we expanded the 42 seeds to 7,551 unique
instances. Finally, the \textit{Sanitizer} category is obtained from
five industrial e-mail address and IPv4 sanitizers.

\begin{table}[t]
    \centering
    \caption{\generator{}-generated instances.}
    \label{tbl:generated}
    \begin{tabular}{|l|l|l|}
        \hline
        \textbf{Name}
            & \textbf{Instances have ...}
            & \textbf{Quantity}
            \\ \hline
        \textit{Concats}
            & A right-heavy, deep tree of concats.
            & 600
            \\ \hline
        \textit{Concats-Balanced}
            & A balanced, deep tree of concats.
            & 100
            \\ \hline
        \textit{Concats-Extracts}
            & A single concat tree, and random character extractions.
            & 600
            \\ \hline
        \textit{Lengths}
            & A single, large length constraint on a variable.
            & 1,000
            \\ \hline
        \textit{Lengths-Concats}
            & Variables and their concats, each with fixed lengths.
            & 500
            \\ \hline
        \textit{Overlaps}
            & A formula of the form A.X = X.B.
            & 100
            \\ \hline
        \textit{Regex}
            & A test for regex membership of arbitrary complexity.
            & 1,200
            \\ \hline
        \textit{Many-Regexes}
            & A test for membership in many random regexes.
            & 600
            \\ \hline
        \textit{Regex-Deep}
            & A test for membership in a regex with many nested operators.
            & 450
            \\ \hline
        \textit{Regex-Pair}
            & A test for membership in one regex, but not another.
            & 600
            \\ \hline
        \textit{Regex-Lengths}
            & A test for membership in a regex, and a length constraint.
            & 600
            \\ \hline
        \textit{Different-Prefix}
            & An equality between two deep concats with different prefixes.
            & 300
            \\ \hline
    \end{tabular}
\end{table}

\begin{table}[t]
    \centering
    \caption{Transformed instances generated by \transformer{}.}
    \label{tbl:transformed}
    \begin{tabular}{|l|l|r|}
        \hline
        \textbf{Name}      & \textbf{Seed}                              & \textbf{Quantity} \\ \hline
        \textit{Amazon}    & Two industrial regex membership instances. & 472 \\ \hline
        \textit{Regex}     & Z3str2 regular expression test suite.      & 7,551 \\ \hline
        \textit{Sanitizer} & 5 e-mail and IPv4 sanitiser examples.      & 1,170 \\ \hline
    \end{tabular}
\end{table}
